5_data_viz

### 2018-05-21 scripts/5_data_viz.Rmd
Re-org Analysis, move viz, etc.

>>>>

<!-- Having calculated the revenues, both short-term and long-term imputed, we now compare the actual (extr), potential and imputed long-term revenue distributions for the short term properties  -->

<!-- ```{r plot_revdens, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5} -->

<!--   # Actual -->
<!--    stra.rev <- str_df.ic[,c('property.id', 'str.act.revenue')] -->
<!--    stra.rev$tenure <- 'Short-Term (Actual)   ' -->
<!--    names(stra.rev)[2] <- 'revenue' -->

<!--   # Potential -->
<!--    strp.rev <- str_df.ic[,c('property.id', 'str.pot.revenue')] -->
<!--    strp.rev$tenure <- 'Short-Term (Potential)   ' -->
<!--    names(strp.rev)[2] <- 'revenue' -->

<!--   # Long-Term -->
<!--    ltr.rev <- str_df.ic[,c('property.id', 'ltr.imp.revenue')] -->
<!--    ltr.rev$tenure <- 'Long-Term   ' -->
<!--    names(ltr.rev)[2] <- 'revenue' -->

<!--   # Combine -->
<!--    revdens.data <- rbind(stra.rev, strp.rev, ltr.rev) -->

<!--   ## Build a plot -->

<!--    rd.plot <- ggplot(revdens.data,  -->
<!--                      aes(x=revenue, fill=tenure, color=tenure)) + -->
<!--      geom_density(alpha=.5) + -->
<!--      scale_fill_manual(values=c(ltr.col, abb.col[2], str.col)) + -->
<!--      scale_color_manual(values=c(ltr.col, abb.col[2], str.col)) + -->
<!--      xlab('\nAnnual Revenue') + -->
<!--      scale_x_continuous(breaks=c(seq(0, 75000, by=25000)), -->
<!--                         labels=c('$0', '$25k', '$50k', '$75k'))+ -->
<!--      theme(legend.position='none', -->
<!--            legend.title = element_blank(), -->
<!--            plot.title = element_text(hjust = 0.5), -->
<!--            axis.text.y = element_blank(), -->
<!--            axis.ticks.y = element_blank(), -->
<!--            axis.title.y=element_blank()) + -->
<!--      coord_cartesian(xlim=c(0, 85000)) -->
<!--      rd.plot <- rd.plot + facet_wrap(~tenure) -->

<!--   ## Plot -->

<!--      rd.plot -->

<!-- ``` -->

<!-- ## Results -->

<!-- Next, we plot the \% of properties that have short-term preference versus the occupancy rate as occupancy rate is an important determinant of short-term preference.  -->

<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->

<!--  ## Set Preference data field -->

<!--   str_df.ic$pref <- str_df.ic$str.act.pref -->

<!--  ## Calculate the percentile fields -->

<!--   str_df.ic$occ.qtl <- makeWtdQtl(str_df.ic$occ.rate,  -->
<!--                                       return.type='rank')  -->
<!--   str_df.ic$rate.qtl <- makeWtdQtl(str_df.ic$med.rate,  -->
<!--                                   return.type='rank')  -->

<!--  ## Calculate raw and percentile occupancies -->

<!--   rawocc.metro <- abbPrefPlot(str_df.ic, -->
<!--                          x.field='occ.rate', -->
<!--                          smooth=TRUE, -->
<!--                          smooth.span=.5) -->

<!--   qtlocc.metro <- abbPrefPlot(str_df.ic, -->
<!--                         x.field='occ.qtl', -->
<!--                         smooth=TRUE, -->
<!--                         smooth.span=.5) -->

<!--    ## Make plots   -->

<!--   # Raw -->
<!--   raw.occ.metro <- ggplot(rawocc.metro$data, -->
<!--                    aes(x=x.var, y=Var))+ -->
<!--     geom_point(alpha=.5, size=.4) + -->
<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
<!--     xlab('\nOccupancy Rate') + -->
<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
<!--     ylab('\nSTR Preferability %') + -->
<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
<!--     theme(legend.position='none') +  -->
<!--     ggtitle('Raw Rates') +  -->
<!--     theme(plot.title = element_text(hjust = 0.5)) -->

<!--   # Quantile -->
<!--   qtl.occ.metro <- ggplot(qtlocc.metro$data, -->
<!--                    aes(x=x.var, y=Var))+ -->
<!--     geom_point(alpha=.5, size=.4) + -->
<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
<!--     xlab('\nOccupancy Rate (Pcntl)') + -->
<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
<!--                        labels=c('0%', '25th', '50th', '75th', '100th')) + -->
<!--     ylab('\nSTR Preferability %') + -->
<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
<!--     theme(legend.position='none') +  -->
<!--     ggtitle('Percentile Rates') +  -->
<!--     theme(plot.title = element_text(hjust = 0.5)) -->

<!--   # Make Plot -->
<!--   ggMultiPlots(raw.occ.metro, qtl.occ.metro, cols=2) -->

<!-- ``` -->

<!-- Next we build a heat map that shows which combinations of occupancy rate and nightly rate are most likely to result in short-term preference. -->

<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->

<!--   rate.hm <- abbHeatMap(str_df.ic, -->
<!--                 x.field='occ.rate', -->
<!--                 y.field='med.rate', -->
<!--                 pref.field='str.act.pref', -->
<!--                 svm=F,  -->
<!--                 alpha.count=T, -->
<!--                 add.points=T, -->
<!--                 fill.colors=c(abb.col[1], abb.col[5])) -->
<!--   rate.hm + ylab('Nightly Rate') -->

<!-- ``` -->

<!-- To make the distinction more clear, we employ a Support Vector Machine to classify the areas into short and long term preference.  -->

<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->

<!--   rate.hm.svm <- abbHeatMap(str_df.ic, -->
<!--                             x.field='occ.rate', -->
<!--                             y.field='med.rate', -->
<!--                             pref.field='str.act.pref', -->
<!--                             svm=T,  -->
<!--                             alpha.count=F, -->
<!--                             add.points=T, -->
<!--                             fill.colors=c(abb.col[1], abb.col[5])) -->
<!--   rate.hm.svm+ ylab('Nightly Rate') -->

<!-- ``` -->

<!-- As the distributions of occupancy rate and nightly rate are not uniform, we standardize these values to a percentile and then replot to give a better sense of the relative level of occupancy rate and nightly rate required for short-term preference. -->

<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->

<!--   qtl.hm <- abbHeatMap(str_df.ic, -->
<!--                 x.field='occ.qtl', -->
<!--                 y.field='rate.qtl', -->
<!--                 pref.field='str.act.pref', -->
<!--                 svm=F,  -->
<!--                 alpha.count=T, -->
<!--                 add.points=T, -->
<!--                 fill.colors=c(abb.col[1], abb.col[5])) -->
<!--   qtl.hm+ ylab('Nightly  (Pcntl)') -->

<!-- ``` -->

<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->

<!--   qtl.hm.svm <- abbHeatMap(str_df.ic, -->
<!--                    x.field='occ.qtl', -->
<!--                    y.field='rate.qtl', -->
<!--                    pref.field='str.act.pref', -->
<!--                    svm=T,  -->
<!--                    alpha.count=F, -->
<!--                    add.points=T, -->
<!--                    quantile=T, -->
<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
<!--   qtl.hm.svm+ ylab('Nightly  (Pcntl)') -->

<!-- ``` -->

<!-- ### Submarkets -->

<!-- Now we move on to looking more deeply at various submarkets.  We start by analyzing the differences between houses and apartments.  -->

<!-- First we make a comparison table of the results.   -->

<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->

<!--  # Make Basic comparison table -->
<!--   pref.table.type <- abbCreateCompTable(ic.df=str_df.ic, -->
<!--                                    split.field='type') -->

<!--  # Limit to the extrapolated pref type -->
<!--   pref.table.type <- pref.table.type[pref.table.type$rev.type == 'Actual', ] -->

<!-- ``` -->

<!-- We then turn this into a simple chart to see the differences. -->

<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->

<!--   ggplot(pref.table.type, aes(x=ID, weights=Var, fill=ID)) +  -->
<!--     geom_bar() + -->
<!--     scale_fill_manual(values=c('red', 'blue')) + -->
<!--     xlab('') + -->
<!--     ylab('% of properties where Airbnb is more profitable') + -->
<!--     scale_y_continuous(breaks=c(0,.25,.5,.75,1), -->
<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
<!--     theme(legend.position='none') -->

<!-- ``` -->

<!-- We then look at the relationship between occ rate and preference.  Before we start though we recalculate the percentiles within each submarket.  -->

<!-- ```{r build_occ_type1, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->

<!--  ## Create dataset -->

<!--   type.data.ic <- str_df.ic -->

<!--   # Id the types -->
<!--   apt.id <- which(str_df.ic$type == 'Apartment') -->
<!--   house.id <- which(str_df.ic$type == 'House') -->

<!--   # Recalculate the percentiles -->
<!--   type.data.ic$occ.qtl[apt.id] <- makeWtdQtl(type.data.ic$occ.rate[apt.id], -->
<!--                                       return.type='rank') -->
<!--   type.data.ic$occ.qtl[house.id] <- makeWtdQtl( -->
<!--     type.data.ic$occ.rate[house.id], return.type='rank') -->

<!--   type.data.ic$rate.qtl[apt.id] <- makeWtdQtl(type.data.ic$med.rate[apt.id], -->
<!--                                   return.type='rank') -->
<!--   type.data.ic$rate.qtl[house.id] <- makeWtdQtl( -->
<!--     type.data.ic$med.rate[house.id], return.type='rank') -->

<!-- ```  -->

<!-- Then we calculate the preference figures -->

<!-- ```{r build_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->

<!--  ## Calc the occ rate numbers -->

<!--   rawocc.type <- abbPrefPlot(type.data.ic, -->
<!--                          x.field='occ.rate', -->
<!--                          split.field='type', -->
<!--                          smooth=TRUE, -->
<!--                          smooth.span=.5 , -->
<!--                          spl.col=c('black', 'grey40')) -->

<!--   pctocc.type <- abbPrefPlot(type.data.ic, -->
<!--                          x.field='occ.qtl', -->
<!--                          split.field='type', -->
<!--                          smooth=TRUE, -->
<!--                          smooth.span=.5 , -->
<!--                          spl.col=c('black', 'grey40')) -->

<!-- ``` -->

<!-- And then plot.  -->

<!-- ```{r plot_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{smocc}Preference vs Occ. Rates: By Type'} -->

<!--  ## Build raw plot -->

<!--   ptr.occ <- ggplot(rawocc.type$data, -->
<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
<!--     geom_point(alpha=.5, size=.4) + -->
<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
<!--     xlab('\nOccupancy Rate') + -->
<!--     scale_color_manual(values=c('black', 'grey60'), -->
<!--                        name='') + -->
<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
<!--     ylab('\nSTR Preferability %') + -->
<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
<!--     theme(legend.position='bottom') +  -->
<!--     ggtitle('Raw Rates') +  -->
<!--     theme(plot.title = element_text(hjust = 0.5)) -->

<!--  ## Build Percentile Plots -->

<!--   ptq.occ <- ggplot(pctocc.type$data, -->
<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
<!--     geom_point(alpha=.5, size=.4) + -->
<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
<!--     xlab('\nOccupancy Rate (Pcntl)') + -->
<!--     scale_color_manual(values=c('black', 'grey60'), -->
<!--                        name='') + -->
<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
<!--                        labels=c('0%', '25th', '50th', '75th', '100th')) + -->
<!--     ylab('\nSTR Preferability %') + -->
<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
<!--     theme(legend.position='bottom') +  -->
<!--     ggtitle('Percentile Rates') +  -->
<!--     theme(plot.title = element_text(hjust = 0.5)) -->

<!--  ## Plot   -->

<!--   ggMultiPlots(ptr.occ, ptq.occ, cols=2) -->

<!-- ``` -->

<!-- Finally, we make percentile SVM heatmaps for both apartments and houses.  -->

<!-- ```{r plot_svm_type, fig.width=8, fig.height=3.5, echo=FALSE, fig.cap='\\label{smhm}Analysis of Percentile Rates: By Type'} -->

<!--  ## Make House SVM Heatmap -->

<!--   house.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type == -->
<!--                                           'House', ], -->
<!--                    x.field='occ.qtl', -->
<!--                    y.field='rate.qtl', -->
<!--                    pref.field='str.act.pref', -->
<!--                    svm=T, -->
<!--                    alpha.count=F, -->
<!--                    add.points=T, -->
<!--                    quantile=T, -->
<!--                    fill.colors=c(abb.col[1], abb.col[5])) + -->
<!--   theme(legend.position='none') + -->
<!--   annotate("text", x = 50, y = 50, label = "Houses", size=9) + -->
<!--   ylab('Nightly Rate (Pcntl)') + -->
<!--   xlab('Occupancy Rate (Pcntl)') -->

<!--  ## Make Apartment SVM Heat Map -->

<!--   apt.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type == -->
<!--                                           'Apartment', ], -->
<!--                    x.field='occ.qtl', -->
<!--                    y.field='rate.qtl', -->
<!--                    pref.field='str.act.pref', -->
<!--                    svm=T, -->
<!--                    alpha.count=F, -->
<!--                    add.points=T, -->
<!--                    quantile=T, -->
<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
<!--   theme(legend.position='none')+ -->
<!--   annotate("text", x = 50, y = 50, label = "Apartments", size=9)+ -->
<!--   ylab('Nightly Rate (Pcntl)') + -->
<!--   xlab('Occupancy Rate (Pcntl)') -->

<!--  ## Plot -->

<!--   ggMultiPlots(house.hm.svm, apt.hm.svm, cols=2) -->

<!-- ``` -->

<!-- #### Geographic Submarkets -->

<!-- We now repeat the three analyses -- table, occupancy plot, heat map -- for the five geographic submarkets. -->

<!-- ```{r table_geo, message=FALSE, warning=FALSE, results='asis', comment=FALSE, cache=TRUE, echo=FALSE, fig.cap='Geographic Submarket Preferability'} -->

<!--  # Make Basic comparison table -->
<!--   pref.table <- abbCreateCompTable(ic.df=str_df.ic, -->
<!--                                    split.field='geo.mrkt') -->

<!--  # Convert to wide format for output -->
<!--   pref.table.wide <- dcast(pref.table, ID ~ rev.type, value.var='Var') -->

<!--  # Limit to the extrapolated pref type -->
<!--   pref.table <- pref.table[pref.table$rev.type == 'Actual', ] -->
<!--   pref.table[ ,1] <- c('City-Core', 'City', 'Suburban', 'Rural', 'Beach') -->
<!--   pref.table[ ,2] <- paste0(sprintf('%.1f', pref.table[ ,2] * 100), '%') -->

<!--  # Fix names   -->
<!--   names(pref.table) <- c('Sub-Market', 'Short-Term Preferable') -->
<!--   options(xtable.comment = FALSE) -->

<!--  ## Make printable table -->

<!--   print(xtable(pref.table[,1:2],  -->
<!--                caption='Geographic Submarket Preferability\n', -->
<!--                digits=1, -->
<!--                align='llr'), -->
<!--         include.rownames=FALSE, -->
<!--         caption.placement='top') -->

<!-- ``` -->

<!-- ```{r build_occ_geo, fig.width=8, fig.height=4, echo=FALSE}  -->

<!--  ## Build data -->

<!--   subm.data.ic <- str_df.ic -->

<!--   # Get IDs -->
<!--   cc.id <- which(str_df.ic$geo.mrkt == 'city-core') -->
<!--   city.id <- which(str_df.ic$geo.mrkt == 'city') -->
<!--   sub.id <- which(str_df.ic$geo.mrkt == 'suburban') -->
<!--   rural.id <- which(str_df.ic$geo.mrkt == 'rural') -->
<!--   beach.id <- which(str_df.ic$geo.mrkt == 'beach') -->

<!--   # Recalc the percentiles -->
<!--   subm.data.ic$occ.qtl[cc.id] <- makeWtdQtl(subm.data.ic$occ.rate[cc.id], -->
<!--                                       return.type='rank') -->
<!--   subm.data.ic$rate.qtl[cc.id] <- makeWtdQtl(subm.data.ic$med.rate[cc.id], -->
<!--                                   return.type='rank') -->

<!--   subm.data.ic$occ.qtl[city.id] <- makeWtdQtl( -->
<!--       subm.data.ic$occ.rate[city.id], return.type='rank') -->
<!--   subm.data.ic$rate.qtl[city.id] <- makeWtdQtl( -->
<!--     subm.data.ic$med.rate[city.id], return.type='rank') -->

<!--   subm.data.ic$occ.qtl[sub.id] <- makeWtdQtl(subm.data.ic$occ.rate[sub.id], -->
<!--                                       return.type='rank') -->
<!--   subm.data.ic$rate.qtl[sub.id] <- makeWtdQtl(subm.data.ic$med.rate[sub.id], -->
<!--                                   return.type='rank') -->

<!--   subm.data.ic$occ.qtl[rural.id] <- makeWtdQtl(subm.data.ic$occ.rate[rural.id], -->
<!--                                       return.type='rank') -->
<!--   subm.data.ic$rate.qtl[rural.id] <- makeWtdQtl(subm.data.ic$med.rate[rural.id], -->
<!--                                   return.type='rank') -->

<!--   subm.data.ic$occ.qtl[beach.id] <- makeWtdQtl(subm.data.ic$occ.rate[beach.id], -->
<!--                                       return.type='rank') -->
<!--   subm.data.ic$rate.qtl[beach.id] <- makeWtdQtl(subm.data.ic$med.rate[beach.id], -->
<!--                                   return.type='rank') -->

<!-- ``` -->

<!-- ```{r plot_occ_geo, fig.width=9, fig.height=4, message=FALSE, warning=FALSE, echo=FALSE, fig.cap='\\label{smocc}Analysis of Percentile Rates: Geographic Submarkets'}  -->

<!--  ## Set colors -->

<!--   sm.col <- abb.col[c(1, 3, 6, 5, 2)]  -->

<!--  ## Create plot data -->

<!--   rawocc.geo <- abbPrefPlot(subm.data.ic, -->
<!--                         x.field='occ.rate', -->
<!--                         split.field='geo.mrkt', -->
<!--                         smooth=TRUE, -->
<!--                         smooth.span=.5 , -->
<!--                         spl.col=sm.col) -->

<!--   pctocc.geo <- abbPrefPlot(subm.data.ic, -->
<!--                          x.field='occ.qtl', -->
<!--                          split.field='geo.mrkt', -->
<!--                          smooth=TRUE, -->
<!--                          smooth.span=.5 , -->
<!--                          spl.col=sm.col) -->

<!--  ## Make plot objects   -->

<!--   smr.occ <- ggplot(rawocc.geo$data, -->
<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
<!--     geom_point(alpha=.5, size=.4) + -->
<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
<!--     xlab('\nOccupancy Rate') + -->
<!--     scale_color_manual(values=sm.col, -->
<!--                        name='') + -->
<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
<!--     ylab('\nSTR Preferability %') + -->
<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
<!--     theme(legend.position='bottom') +  -->
<!--     ggtitle('Raw Rates') +  -->
<!--     theme(plot.title = element_text(hjust = 0.5)) -->

<!--   smq.occ <- ggplot(pctocc.geo$data, -->
<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
<!--     geom_point(alpha=.5, size=.4) + -->
<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
<!--     xlab('\nOccupancy Rate (Pcntl)') + -->
<!--     scale_color_manual(values=sm.col, -->
<!--                        name='') + -->
<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
<!--                        labels=c('0%', '25th', '50th', '75th', '100th')) + -->
<!--     ylab('\nSTR Preferability %') + -->
<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
<!--     theme(legend.position='bottom') +  -->
<!--     ggtitle('Percentile Rates') +  -->
<!--     theme(plot.title = element_text(hjust = 0.5)) -->

<!--  ## Plot   -->

<!--   ggMultiPlots(smr.occ, smq.occ, cols=2) -->

<!-- ``` -->

<!-- ```{r build_svm_geo, fig.width=8, fig.height=4, echo=FALSE, fig.cap='Analysis of Percentile Rates: Metro Level'} -->

<!--   # Build the SVM Heatmaps -->

<!--   core.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
<!--                                           'city-core', ], -->
<!--                    x.field='occ.qtl', -->
<!--                    y.field='rate.qtl', -->
<!--                    pref.field='str.act.pref', -->
<!--                    svm=T, -->
<!--                    alpha.count=F, -->
<!--                    add.points=T, -->
<!--                    quantile=T, -->
<!--                    fill.colors=c(abb.col[1], abb.col[5])) + -->
<!--   theme(legend.position='none') + -->
<!--     ylab('') + -->
<!--     xlab('') + -->
<!--   annotate("text", x = 50, y = 50, label = "City-Core", size=9) -->

<!--   city.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
<!--                                           'city', ], -->
<!--                    x.field='occ.qtl', -->
<!--                    y.field='rate.qtl', -->
<!--                    pref.field='str.act.pref', -->
<!--                    svm=T, -->
<!--                    alpha.count=F, -->
<!--                    add.points=T, -->
<!--                    quantile=T, -->
<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
<!--   theme(legend.position='none')+ -->
<!--     ylab('') + -->
<!--     xlab('')+ -->
<!--   annotate("text", x = 50, y = 50, label = "City", size=9) -->

<!--   sub.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
<!--                                           'suburban', ], -->
<!--                    x.field='occ.qtl', -->
<!--                    y.field='rate.qtl', -->
<!--                    pref.field='str.act.pref', -->
<!--                    svm=T, -->
<!--                    alpha.count=F, -->
<!--                    add.points=T, -->
<!--                    quantile=T, -->
<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
<!--   theme(legend.position='none')+ -->
<!--     ylab('') + -->
<!--     xlab('')+ -->
<!--   annotate("text", x = 50, y = 50, label = "Suburban", size=9) -->

<!--   rural.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
<!--                                           'rural', ], -->
<!--                    x.field='occ.qtl', -->
<!--                    y.field='rate.qtl', -->
<!--                    pref.field='str.act.pref', -->
<!--                    svm=T, -->
<!--                    alpha.count=F, -->
<!--                    add.points=T, -->
<!--                    quantile=T, -->
<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
<!--   theme(legend.position='none')+ -->
<!--     ylab('') + -->
<!--     xlab('')+ -->
<!--   annotate("text", x = 50, y = 50, label = "Rural", size=9) -->

<!--   beach.hm.svm <- abbHeatMap(subm.data.ic[subm.data.ic$geo.mrkt == -->
<!--                                           'beach', ], -->
<!--                    x.field='occ.qtl', -->
<!--                    y.field='rate.qtl', -->
<!--                    pref.field='str.act.pref', -->
<!--                    svm=T, -->
<!--                    alpha.count=F, -->
<!--                    add.points=T, -->
<!--                    quantile=T, -->
<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
<!--   theme(legend.position='none')+ -->
<!--     ylab('') + -->
<!--     xlab('')+ -->
<!--   annotate("text", x = 50, y = 50, label = "Beach", size=9) -->

<!-- ``` -->

<!-- ```{r plot_svm_geo, message=FALSE, warning=FALSE, fig.width=8, fig.height=8, echo=FALSE, fig.cap='\\label{smhmps}Geographic Submarket Heatmaps'} -->

<!--   ggMultiPlots(core.hm.svm, city.hm.svm, sub.hm.svm, -->
<!--                rural.hm.svm, beach.hm.svm, cols=2) -->

<!-- ``` -->

## Sensitivity

### Potential Revenue

To test for the sensitivity of the result to the revenue type, we re-do some of the intial data vizs.  First we build a new preference table looking at the submarkets of type and geography.

```{r pot_table, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.cap='Potential Short-Term Preference'}

 # Make Basic comparison table of type
  tpref.table <- abbCreateCompTable(ic.df=str_df.ic,
                                    split.field='type')
 # Extract Potential Results
  tpref.table <- tpref.table[tpref.table$rev.type == 'Potential', ]

 # Make baseic comparison table of submarkets  
  spref.table <- abbCreateCompTable(ic.df=str_df.ic,
                                    split.field='geo.mrkt')

 # Extract potential results  
  spref.table <- spref.table[spref.table$rev.type == 'Potential', ]

 # Combine and round  
  st.table <- rbind(tpref.table, spref.table)
  st.table[,2] <- paste0(sprintf('%.1f', st.table[,2]*100), '%')

 ## Fix names and print

  names(st.table) <- c('Sub-Market', 'Short-Term Preferable')
  options(xtable.comment = FALSE)
  print(xtable(st.table[,1:2], 
               caption='Potential Revenue Preferability\n',
               digits=1, align='llr'),
               include.rownames=FALSE,
               caption.placement='top',
               hline.after=c(-1, 0, 2, 7, 7))

Next we recrate the SVM percentile heat maps.

```{r pot_svm, results='asis', echo=FALSE, message=FALSE, comment=FALSE}

 ## create data and re-estimate the percentiles

  pot.data.ic <- str_df.ic

  pot.data.ic$occ.qtl <- makeWtdQtl(pot.data.ic$pot.occ.rate, return.type='rank')

 ## Make the pecentile heatmap

  pqtl.hm <- abbHeatMap(pot.data.ic,
                x.field='occ.qtl',
                y.field='rate.qtl',
                pref.field='str.pot.pref',
                svm=F, 
                alpha.count=T,
                add.points=T,
                fill.colors=c(abb.col[1], abb.col[5]))
  pqtl.hm <- pqtl.hm + ylab('Nightly Rate (Qtl)')

 ## Make percentile SVM heatmap

  pqtl.hm.svm <- abbHeatMap(pot.data.ic,
                   x.field='occ.qtl',
                   y.field='rate.qtl',
                   pref.field='str.pot.pref',
                   svm=T, 
                   alpha.count=F,
                   add.points=T,
                   quantile=T,
                   fill.colors=c(abb.col[1], abb.col[5]))
  pqtl.hm.svm <- pqtl.hm.svm + ylab('Nightly Rate (Pcntl)')+
    xlab('Occupancy Rate (Pcntl)') +
  annotate("text", x = 50, y = 50, label = "Potential", size=9)

 ## Add annotations to previous SVM

  qtl.hm.svm.p <- qtl.hm.svm +
  annotate("text", x = 50, y = 50, label = "Actual", size=9)

```{r plot_pot_svm, results='asis', echo=FALSE, message=FALSE, comment=FALSE, fig.height=3.5, fig.cap='\\label{pothm}Heatmaps of Short-Term Preference'}

  ggMultiPlots(qtl.hm.svm.p, pqtl.hm.svm, cols=2)

 ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  ggplot(str_tdf, aes(x=block_rate)) + 
    geom_density(fill=str_col, color=str_col) +
    ylab('Frequency\n') + 
    xlab('\n% of Time Property is Blocked') +
    scale_x_continuous(breaks=seq(0,1,.2),
                       labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
      ggtitle('Host Block Rate Frequency\n') +
      theme(plot.title = element_text(hjust = 0.5)) +
      theme(axis.text.y=element_blank(),
          axis.ticks.y=element_blank())

  # Make Plot
  png(file=paste0(fig.path, 'dataanys_hostblock.png'), width = 480, height = 280, 
      bg='transparent')

    host.block.freq

  dev.off()

  save(host.block.freq, file=paste0(fig.path, 'hostblockfreq.RData'))

```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  block.rate.period <- ggplot(str_df, aes(x=block.rate, y=nbr.block*extr.par)) + 
  geom_point(fill=str.col, color=str.col, size=.2) +
  ylab('Nbr of Blocked Periods\n') + 
  xlab('\n% of Time Property is Blocked') +
  scale_x_continuous(breaks=seq(0, 1, .2),
                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
    theme(plot.title = element_text(hjust = 0.5))

  # Make Plot
  png(file=paste0(fig.path, 'dataanys_blockrateperiod.png'), width = 480, height = 280, 
      bg='transparent')

    block.rate.period

  dev.off()

  block.rate.period

  save(block.rate.period, file=paste0(fig.path, 'blockrateperiod.RData'))

```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  str_tdf$blockpertime <- round(str_tdf$nbr_block * str_tdf$extr_par, 1)

  str_tdf$host_type <- 'Unknown'
  str_tdf$host_type[str_tdf$blockpertime > 12] <- 'Multi-Platform User'
  str_tdf$host_type[str_tdf$block_rate <= .25] <- 'Profit Seeker'
  str_tdf$host_type[str_tdf$block_rate >= .75] <- 'Opportunistic Sharer'
  str_tdf$host_type <- factor(str_tdf$host_type,
                              levels=c('Profit Seeker', 'Opportunistic Sharer', 
                                        'Multi-Platform User', 'Unknown'))

 ggplot(str_tdf, 
       aes(x=block_rate, y=blockpertime, color=host_type)) + 
  geom_point(alpha=.5, size=.8, shape=16) +
  ylab('Number of Blocked Periods\n') + 
  xlab('\n% of Time Property is Blocked') +
      ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +

    scale_x_continuous(breaks=seq(0, 1, .2),
                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    scale_color_manual(values=c(col.df$rgb[2], col.df$rgb[4], col.df$rgb[7], col.df$rgb[9])) + 
    theme(legend.position='bottom',
           legend.title = element_blank(),
         plot.title = element_text(hjust = 0.5))+
     guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1)))
  # Make Plot
  png(file=paste0(fig.path, 'dataanys_hosttype.png'), width = 480, height = 280, 
      bg='transparent')

    host.type

  dev.off()

  host.type

  save(host.type, file=paste0(fig.path, 'hosttype.RData'))

See the counts of each group

```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

host.type.bar <- ggplot(str_df.ic, aes(host.type, fill=host.type)) +
  geom_bar() +
  scale_fill_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9]))+
  theme(legend.position='none') +
  ylab('Frequency\n') + 
  xlab('\nHost Type') +
  ggtitle('Short Term Host Types') + 
  theme(plot.title = element_text(hjust = 0.5))

  # Make Plot
  png(file=paste0(fig.path, 'dataanys_hosttypebar.png'), width = 480, height = 280, 
      bg='transparent')

    host.type.bar

  dev.off()

  host.type.bar

  save(host.type.bar, file=paste0(fig.path, 'hosttypebar.RData'))

We then re-estimate the preference table.

```{r host_table, results='asis', message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE}

 # Make Basic comparison table
  apref.table <- abbCreateCompTable(ic.df=str_df.ic,
                                    split.field='host.type')

 # Limit to the extrapolated pref type
  hpref.table <- apref.table[apref.table$rev.type == 'Actual', ]
  phpref.table <- apref.table[apref.table$rev.type == 'Potential', ]
  hpref.table <- hpref.table[,1:2]
  hpref.table[,3] <- phpref.table[,2]
  hpref.table[,2] <- paste0(sprintf('%.1f', hpref.table[,2]*100), '%')
  hpref.table[,3] <- paste0(sprintf('%.1f', hpref.table[,3]*100), '%')
